Proposed Solution

### 2016-01-29 evaluation.tex

To evaluate our tool, we take a subset of 20 canonical benchmarks for configuration errors~\cite{yin11anempirical, configdataset} which are supported by our tool. Table~\ref{table:res} contains an evaluation summary.
We do not report the running times, since they are negligible: even when
 running in the interpreter mode, files are analyzed instantaneously. We spent approximately 30 second on learning the rules. When we run the compiled version, we need for lerning and verification 
combined less than 5 seconds. Our focus is usefulness of the tool: its 
 ability to detect configuration errors and the number of false positives.
 For every benchmark class we took five examples. The middle column represents the number of detected errors, while the right column represents the number of returned false positives per each benchmark.

>>>>

To evaluate our tool, we take a subset of 20 benchmarks from an existsing dataset of configuration errors~\cite{yin11anempirical, configdataset} which are supported by our tool. Table~\ref{table:res} contains an evaluation summary.
We do not report the running times, since they are negligible: even when
 running in the interpreter mode, files are analyzed instantaneously. We spent approximately 30 second on learning the rules. When we run the compiled version, we need for lerning and verification 
combined less than 5 seconds. Our focus is usefulness of the tool: its 
 ability to detect configuration errors and the number of false positives.
 For every benchmark class we took five examples. The middle column represents the number of detected errors, while the right column represents the number of returned false positives per each benchmark.
